Instructions for COLING-2016 Proceedings

### 2016-07-15 paper/coling2016.tex
coling

\documentclass[conference,compsoc]{IEEEtran}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

\usepackage{bm}%used for bm
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath} %used for maths symbols
\usepackage{amssymb}%used for empty set symbol
\usepackage{url}
\usepackage{xcolor}% or package color

%used for quotes
\usepackage{epigraph}
\setlength\epigraphwidth{\columnwidth}
\setlength\epigraphrule{0pt}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}

%主动感知的
\title{Normal States Training for High Accuracy Event Detection}

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.

\section{Introduction}
%\textit{``To study the abnormal is the best way of understanding the normal."}---William James
%\textit{``The unpredictable or the rare is more newsworthy than the routine."}---Allan Bell

%The event detection task always tries to find out the newsworthy messages from cyberspace. 
With the increasing of cyberspace data, there is a growing need for detecting events accurately. Detecting events can mainly benefit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.

@@

\textbf{detected events related to micro-blog}
\ \
By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).

>>>>

%
% File coling2016.tex
%
% Contact: mutiyama@nict.go.jp
%%
%% Based on the style files for COLING-2014, which were, in turn,
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{coling2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{bm}%used for bm
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{amssymb}%used for empty set symbol
\usepackage{amsmath} %used for maths symbols

\usepackage{graphics}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\title{Instructions for COLING-2016 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
\end{abstract}

\section{Introduction}
\label{intro}

With the increasing of cyberspace data, there is a growing need for detecting events accurately. Detecting events can mainly benefit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.

@@
